brados: declarative, programmable object storage

### 2016-05-25 paper.tex
cap update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\begin{table}[ht]
\centering
\begin{tabularx}{\columnwidth}{|X|l|l|l|}
\hline
Category & Specialization & Methods \\ \hline
\multirow{2}{*}{Locking} & Shared & \multirow{2}{*}{6} \\
                         & Exclusive & \\ \hline
\multirow{3}{*}{Logging} & Replica & 3 \\
                         & State & 4 \\
                         & Timestamped & 4 \\ \hline
Garbage Collection & Ref. Counting & 4 \\ \hline
\multirow{4}{*}{Metadata} & RBD & 37 \\
 & RGW & 27 \\
 & User & 5 \\
 & Version & 5 \\ \hline
\end{tabularx}
\caption{A variety of RADOS object storage classes exist that expose reusable
interfaces to applications.}
\label{tab:objclass-cats}
\end{table}

A critical step in the development of application-specific object interfaces
is deciding how to best make use of the native object interfaces. For instance
if an application stores an image in an object, it may also extract and store
EXIF metadata as key-value pairs in the object key-value database.  However,
depending on the application needs it may be sufficient or offer a performance
advantage to store this metadata as a header within the bytestream. In the remainder
of this section we will explore the challenges associated with these design questions.

>>>>

\begin{table}[ht]
\centering
\begin{tabularx}{\columnwidth}{|X|l|l|l|}
\hline
Category & Specialization & Methods \\ \hline
\multirow{2}{*}{Locking} & Shared & \multirow{2}{*}{6} \\
                         & Exclusive & \\ \hline
\multirow{3}{*}{Logging} & Replica & 3 \\
                         & State & 4 \\
                         & Timestamped & 4 \\ \hline
Garbage Collection & Ref. Counting & 4 \\ \hline
\multirow{4}{*}{Metadata} & RBD & 37 \\
 & RGW & 27 \\
 & User & 5 \\
 & Version & 5 \\ \hline
\end{tabularx}
\caption{A variety of RADOS object storage interfaces exist that expose reusable
    interfaces to applications. The \emph{locking}, \emph{logging}, and
    \emph{GC} categories are generic, while high-level services like \emph{RBD} and
    \emph{RGW} implement application-specific metadata management interfaces.}
\label{tab:objclass-cats}
\end{table}

A critical step in the development of application-specific object interfaces
is deciding how to best make use of the native object interfaces. For instance
if an application stores an image in an object, it may also extract and store
EXIF metadata as key-value pairs in the object key-value database.  However,
depending on the application requirements it may be sufficient or offer a performance
advantage to store this metadata as a header within the bytestream. In the remainder
of this section we will explore the challenges associated with these design questions.
